Generating Simulated Data

### 2021-02-04 docs/SimData.Rmd
rerun census surveys and write msspm bio files

This was run previously but true datasets are generated as follows, with outputs saved to the `atlantisoutput` folder (not kept on github due to size):

@@

NOBAom <- om_init(here("simulated-data/config/NOBA2config.R"))

@@

@@

NOBAom_ms_diet <- om_diet(config = here("config", "NOBA2config.R"),
                          dietfile = "NOBADetDiet.gz",
                          usersurvey = c(here("config/mssurvey_spring.R"), 
                                         here("config/mssurvey_fall.R")), 
                          omlist_ss = NOBAom_ms, 
                          n_reps = 1, 
                          save = TRUE)

@@

##

>>>>

True datasets are generated as follows, using `atlantisom` wrapper functions `om_init` to assemble initial true atlantis data, `om_species` to subset true data for desired species, `om_index` to generate survey biomass and total catch biomass indices, `om_comps` to generate age and length compositions and average weight at age from surveys and fisheries, and `om_diet` to generate diet from surveys. Outputs are saved to the `atlantisoutput` folder (not kept on github due to size):

@@

NOBAom <- om_init(here("simulated-data/config/NOBA2Config.R"))

@@

#need to change internal call to source in atlantisom om_index om_comps and om_diet functions
#expecting a config folder in same directory as rmd
#this is a workaround

dir.create(file.path(here("docs/config")))

file.copy(here("simulated-data/config/omdimensions.R"), here("docs/config/omdimensions.R"))

@@

NOBAom_ms_diet <- om_diet(config = here("simulated-data/config", "NOBA2config.R"),
                          dietfile = "NOBADetDiet.gz",
                          usersurvey = c(here("simulated-data/config/mssurvey_spring.R"), 
                                         here("simulated-data/config/mssurvey_fall.R")), 
                          omlist_ss = NOBAom_ms, 
                          n_reps = 1, 
                          save = TRUE)

unlink(here("docs/config"), recursive = TRUE)
```

Example input files are in the `model-input-files` directory. First we write the fairly simple biomass and catch inputs for the multispecies surplus production model MSSPM from our census survey outputs.

```{r write-msspm}

o.name <- here("simulated-data/msinput/msspm/")

#read in survey biomass data
survObsBiom <- read_savedsurvs(d.name, 'survB') #reads in all surveys

#multiple surveys named in list object, use as filename
for(s in names(survObsBiom)){
  #arrange into wide format: year, Species1, Species2 ... and write csv
  svbio <- survObsBiom[[s]][[1]] %>%
    calc_timestep2time(d.name, ., run.prm.file) %>%
    dplyr::select(species, year, atoutput) %>%
    tidyr::spread(species, atoutput) %>%
    write_csv(paste0(o.name,s,".csv"))
}

#read in catch data
read_savedfisheries <- function(dir, type){

  datlook <- data.frame(dattype = c('Catch', 'catchAge', 'catchLen', 'catchWtage', 'catchAnnAge', 'catchAnnWtage'),
                        pattern = c("*fishCatch.rds", "*fishObsAgeComp.rds", "*fishObsLenComp.rds", "*fishObsWtAtAge.rds",
                                    "*fishObsFullAgeComp.rds", "*fishObsFullWtAtAge.rds"))

  fisheries <- list.files(path=dir, pattern = as.character(datlook$pattern[datlook$dattype %in% type]), full.names = TRUE)

  fishery.name <-  str_match(fisheries, paste0(scenario.name,"_\\s*(.*?)\\s",datlook$pattern[datlook$dattype==type]))[,2]

  dat <- lapply(fisheries, readRDS)

  names(dat) <- fishery.name

  return(dat)
}

catchbio_ss <- read_savedfisheries(d.name, 'Catch')

#arrange into wide format: Year, Species1, Species2 ...

#write to csv

#write readme for metadata

@@

## Generating a survey dataset
